### 2025-10-02 cognitive-bias.qmd
20251001 - copyediting

It is important consider whether such a string of strong performances are outliers and if the player may, in future games, [regress to the mean](#sec-fallaciesRegression).
When considering whether strong performances are outliers and may [regress to the mean](#sec-fallaciesRegression), it is valuable to consider whether the player's health, skill, or situation has appreciably changed (compared to the player's earlier, weaker performances).
Is the player finally fully healthy?
Has the player appreciably improved in some skill that will benefit them in future games?
Has the player's long-term situation improved, such as moving up the depth chart, or receiving more carries/targets that is not tied to a specific opponent or game script?
Or, alternatively, do the improvements appear to be driven by transient, game-specific factors, such as a the health of a teammate, the opponents they played, or the game script that ensued?
If long-term outlook of the player has appreciably changed due to changes in the [fundamentals of a player's value](#sec-playerEvaluation), such as their [health](#sec-evalHealth), [skill](#sec-skill), or [situation](#sec-evalSituation), it is less likely that such performance improvements will [regress](#sec-fallaciesRegression) over the long run.

@@

In conclusion, there are many [heuristics](#sec-heuristics), [cognitive biases](#sec-cognitiveBiases), and [fallacies](#sec-fallacies) that people engage in when making judgments and predictions.
It is prudent to be aware of these common biases and to work to counteract them.
For instance, look for information that challenges or disconfirms your beliefs, and work to incorporate this information into your beliefs.
Do your best to pursue observation, data analysis, and data interpretation with an open mind.
You never know what important information you might discover if you go in with an open mind.
Pay attention to [fundamentals of a player's value](#sec-playerEvaluation), such as their [health](#sec-evalHealth), [skill](#sec-skill), or [situation](#sec-evalSituation) when considering whether a player's performance may [regress to the mean](#sec-fallaciesRegression).
If the strong performances appear to be driven by transient, game-specific factors, such as a the health of a teammate, the opponents they played, or the game script that ensued, future performances may be more likely to [regress to the mean](#sec-fallaciesRegression).
In general, people tend to be [overconfident](#sec-cognitiveBiasesOverconfidence) in their predictions.
There is considerable luck in fantasy football.
Approach the task of prediction with humility; no one is consistently able to accurately predict how well players will perform.

>>>>

It is important consider whether such a string of strong performances are outliers and if the player may, in future games, [regress to the mean](#sec-fallaciesRegression).
When considering whether strong performances are outliers and may [regress to the mean](#sec-fallaciesRegression), it is valuable to consider whether the player's health, skill, or situation has appreciably changed (compared to the player's earlier, weaker performances).
Is the player finally fully healthy?
Has the player appreciably improved in some skill that will benefit them in future games?
Has the player's long-term situation improved, such as moving up the depth chart, or receiving more carries/targets that is not tied to a specific opponent or game script?
Or, alternatively, do the improvements appear to be driven by transient, game-specific factors, such as the health of a teammate, the opponents they played, or the game script that ensued?
If long-term outlook of the player has appreciably changed due to changes in the [fundamentals of a player's value](#sec-playerEvaluation), such as their [health](#sec-evalHealth), [skill](#sec-skill), or [situation](#sec-evalSituation), it is less likely that such performance improvements will [regress](#sec-fallaciesRegression) over the long run.

@@

In conclusion, there are many [heuristics](#sec-heuristics), [cognitive biases](#sec-cognitiveBiases), and [fallacies](#sec-fallacies) that people engage in when making judgments and predictions.
It is prudent to be aware of these common biases and to work to counteract them.
For instance, look for information that challenges or disconfirms your beliefs, and work to incorporate this information into your beliefs.
Do your best to pursue observation, data analysis, and data interpretation with an open mind.
You never know what important information you might discover if you go in with an open mind.
Pay attention to [fundamentals of a player's value](#sec-playerEvaluation), such as their [health](#sec-evalHealth), [skill](#sec-skill), or [situation](#sec-evalSituation) when considering whether a player's performance may [regress to the mean](#sec-fallaciesRegression).
If the strong performances appear to be driven by transient, game-specific factors, such as the health of a teammate, the opponents they played, or the game script that ensued, future performances may be more likely to [regress to the mean](#sec-fallaciesRegression).
In general, people tend to be [overconfident](#sec-cognitiveBiasesOverconfidence) in their predictions.
There is considerable luck in fantasy football.
Approach the task of prediction with humility; no one is consistently able to accurately predict how well players will perform.
